Behavior Driven Development in Haskell

### 2012-05-24 paper.tex
adding labels.

\begin{itemize}
\item Introduced {\tt doctest} from Python community to Haskell community
and integrated it with QuickCheck (Section XXX)
\item Introduced {\tt hspec} from Ruby community to Haskell community and
integrated it with QuickCheck (Section XXX)
\item Show best current practice of design/documentation/tests (Section XXX)
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Visible behavior}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Internal behavior}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{hspec}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Best current practice}

>>>>

\begin{itemize}
\item Introduced {\tt doctest} from Python community to Haskell community
and integrated it with QuickCheck
(Section \ref{sec:Visible-behavior} and Section \ref{sec:doctest})
\item Introduced {\tt hspec} from Ruby community to Haskell community and
integrated it with QuickCheck
(Section \ref{sec:Internal-behavior} and Section \ref{sec:hspec})
\item Show best current practice of behavior driven development in Haskell (Section \ref{ref:Best-current-practice})
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Visible behavior}
\label{sec:Visible-behavior}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Internal behavior}
\label{sec:Internal-behavior}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{hspec}
\label{sec:hspec}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Best current practice}
\label{ref:Best-current-practice}
